Examples

### 2021-01-03 examples.tex

\begin{example}
    Let $G = \SL_3$ and $\uvi = 121$.
    Take $n_\bullet^1 = (1,0,0)$, and $n_\bullet^2 = (1,0,1)$ or $(0,1,0)$. So $\mu_1, = (2,2,1)$, $\lambda_1 = (3,1,1)$ and $\mu_2 = (1,1,1)$, $\lambda_2 = (2,1,0)$. \acom{We should show that order does not matter.}
    Then $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements 
    \[
    \begin{bmatrix}
        0 & 1 & 0 \\
        0 & 0 & 1 \\
        0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
          &   &   & 0 & 1 & 0 \\
          &   &   & 0 & 0 & 1 \\
          &   &   & 0 & 0 & s & c_1 & 0 \\
          &   &   &   &   &   & 0 & 1 \\
          &   &   &   &   &   & 0 & s 
    \end{bmatrix}    
    \]
    and zero eigenspace conforming to the shape 
    \[
    \lambda_1 = \yng(3,1,1)    
    \] 
    is made of three cycles
    \begin{align*}
        a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
        e_4 & \\
        e_7 & 
    \end{align*}
    while the $s$-eigenspace confirming to the shape 
    \[
    \lambda_2 = \yng(2,1)    
    \]
    is made of the two cycles 
    \begin{align*}
        e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
        e_4 + s e_5 + s^2 e_6 & 
    \end{align*}
    assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}
\end{document}

>>>>

\begin{example}
    Let $G = \SL_3$ and $\uvi = 121$.
    Take $n_\bullet^1 = (1,0,0)$, and $n_\bullet^2 = (1,0,1)$ or $(0,1,0)$. So $\mu_1, = (2,2,1)$, $\lambda_1 = (3,1,1)$ and $\mu_2 = (1,1,1)$, $\lambda_2 = (2,1,0)$. \acom{We should show that order does not matter.}
    Then $\TT_{\mu_1,\mu_2}^+\cap\OO_{\lambda_1,\lambda_2}$ is made up of elements 
    \[
    \begin{bmatrix}
        0 & 1 & 0 \\
        0 & 0 & 1 \\
        0 & 0 & s & 0 & a_2 & a_3 & b_1 & b_2 \\
          &   &   & 0 & 1 & 0 \\
          &   &   & 0 & 0 & 1 \\
          &   &   & 0 & 0 & s & c_1 & 0 \\
          &   &   &   &   &   & 0 & 1 \\
          &   &   &   &   &   & 0 & s 
    \end{bmatrix}    
    \]
    and zero eigenspace conforming to the shape 
    \[
    \lambda_1 = \yng(3,1,1)    
    \] 
    is made of three cycles
    \begin{align*}
        a_2 e_1 &\leftarrow a_2e_2 - s e_4 \leftarrow a_2 e_3 - s e_5 \\
        e_4 & \\
        e_7 & 
    \end{align*}
    while the $s$-eigenspace confirming to the shape 
    \[
    \lambda_2 = \yng(2,1)    
    \]
    is made of the two cycles 
    \begin{align*}
        e_1 + se_2 +s^2 e_3 & \leftarrow e_2 + 2se_3 + e_7 + se_8 \\
        e_4 + s e_5 + s^2 e_6 & 
    \end{align*}
    assuming $b_2 = s$ and $a_2 + sa_3 = 0$.
\end{example}

\begin{example}
Let
    \[
    \begin{aligned}
        \lambda_1 &= (2,0,0,0) & \mu_1 &= (1,1,0,0) \\
        \lambda_2 &= (2,2,1,0) & \mu_2 &= (3,2,1,1)
    \end{aligned}
    \]
so $\lambda_1 - \mu_1 = \alpha_1$ and $\lambda_2 - \mu_2 = \alpha_2 + \alpha_3$. We have the following young tableaux:
\[
\tau_1 = \young(12) \hspace{5mm}
\tau_2 = \young(11,23,4) \hspace{5mm}
\tau_2' = \young(11,24,3)
\]
where $\tau_1$ corresponds to the module $S_1$, $\tau_2$ corresponds to the module $2\rightarrow 3$, and $\tau'_2$ corresponds to the module $2 \leftarrow 3$.

The matrix we are considering is 
\[
X = \begin{bmatrix}
    0 & 1 \\
     & 0 & 1 \\
     & -s^2 & 2s & a & b & c & d \\
     & & & 0 & 1 \\
     & & & & s & e & f \\
     & & & & & s & g \\
     & & & & & & s
\end{bmatrix}
\]
such that $\dim E_0 = 2$, $\dim \ker X = 1$, $\dim E_s = 5$, and $\dim \ker (X-sI) = 3$ where $E_0$ and $E_s$ are the $0$- and $s$-generalized eigenspaces.

We see that the two-cycle in $E_0$ is 
\[
\left\{ X\left(e_2 + \frac{s^2}{a}e_4\right), e_2 + \frac{s^2}{a}e_4 \right\}
= \left\{e_1, e_2 + \frac{s^2}{a}e_4 \right\}.
\]

As $\tau_2$ and $\tau'_2$ both share $\young(11,2)$, we can find a 2-cycle from just the upper-left $3\times3$ block, and an additional vector in $\ker(X-sI)$ from the upper-left $5\times5$-submatrix. The 2-cycle from the $3 \times 3$ block is
\[
\left\{e_1 + se_2 + s^2e_3, -\frac{2}{s}e_1 - e_2 \right\}.
\]
The additional vector in $\ker(X-sI)$ is $e_4 + se_5$ and this requires $a+sb=0$.

Now consider the case that the young diagram we are working with is $\tau_2$. Then we have $e_4 + se_5$ part of a 2-cycle that can be found by looking at the upper-left $6 \times 6$-submatrix. We find that the 2-cycle is
\[
\left\{e_4 + se_5, -\frac{1}{s}e_4 + \frac{s}{e}e_6 \right\}
\]
and this requires that $ae - s^2c = 0$.

The last vector in $\ker(X-sI)$ comes from the entire $X-sI$ and we see it is $-fe_6 + ee_7$, which requires $g=0$ and $ed-cf=0$.

For the case $\tau'_2$, we start with find the third vector in $\ker(X-sI)$ from the upper-left $6 \times 6$-submatrix. We see that it is $e_6$, which requires $c = 0$ and $e = 0$.

For the remaining 2-cycle, we note that $e_4 + se_5 \notin \col(X-sI)$ but $e_6 \in \col(X-sI)$ so our 2-cycle is
\[
\left\{ e_6, \frac{1}{g} e_7 \right\}
\]
which requires $d = 0$ and $f = 0$.

From the minimal polynomial, we have $X^2 (X-sI)^2 = 0$ which gives us the equations
\[
a+sb = cs+eb = bf+cg+ds = esg = 0.
\]
Taking $s\rightarrow 0$, we have the following equations for our two cases of $\tau_2$ and $\tau'_2$:
\[
\begin{array}{c|c}
    \tau_2 & \tau'_2 \\ \hline
    a = 0 & a = 0 \\
    g = 0 & c = 0 \\
    eb = 0 & d = 0 \\
    bf = 0 & e = 0 \\
    ed-cf = 0 & f = 0
\end{array}
\]

For the $\tau_2$ case, the coordinate ring is 
\[
\frac{\CC[a,b,c,d,e,f,g]}{\langle a,g,eb,bf,ed-cf \rangle}
\cong \frac{\CC[b,c,d,e,f]}{\langle eb,bf,ed-cf \rangle}
= \frac{\CC[b,c,d,e,f]}{\langle e,f \rangle \cap \langle b,ed-cf \rangle}
\]
Hence the associated algebraic set is reducible with two irreducible components. The component corresponding to the ideal $\langle e,f \rangle$ is $\AA^3$, which corresponds to $\PP^3$, while the ideal $\langle b,ed-cf \rangle$ corresponds to the toric variety whose toric polytope is a square-based pyramid.

As $\tau_2$ corresponds to the module $2 \rightarrow 3$, the irreducible components should correspond to the modules $P_1 = 1 \rightarrow 2 \rightarrow 3$ and $1 \leftarrow 2 \rightarrow 3$. Indeed, the MV cycle corresponding to $P_1$ is the Grassmannian $Gr(1,4) \cong \PP^3$ and for $1 \leftarrow 2 \rightarrow 3$, we do get a toric variety with polytope the square-based pyramid.

However for the $\tau'_2$ case, the coordinate ring is 
\[
\frac {\CC[a,b,c,d,e,f,g]}{\langle a,c,d,e,f \rangle}
\cong \CC[b,g]
\]
which corresponds to $\AA^2$. Since $\tau'_2$ corresponds to the module $2\leftarrow 3$, we expect two irreducible components corresponding to the modules $P_3 = 1 \leftarrow 2 \leftarrow 3$ and $1 \rightarrow 2 \leftarrow 3$. $P_3$ corresponds to the variety $Gr(3,4) \cong \PP^3$ and $1 \rightarrow 2 \leftarrow 3$ also corresponds to a toric variety whose polytope is a square-based pyramid (?).
\end{example}
\end{document}
